Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-11 paper/Paper.tex
updates through section 4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{WEST Code Specifications} \label{specs}
The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
{Github} repository. The MLTL syntax for our program is given as the context free grammar below. In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively. $\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively. Note that the last comma listed is not a typo and indeed part of the alphabet. \\
\textbf{Alphabet}: 
\begin{align*}
    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `>' ,}\\
    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
\end{align*}

@@

In the grammar, associative propositional connectives (\textit{Assoc\_Prop\_conn}) are included for the ease of the user. Given well-formed formulas $\phi_1, \phi_2, \phi_3$, the following formula in prefix notation $(\lor[\phi_1, \phi_2, \phi_3])$ is parsed into $((\phi_1 \lor \phi_2) \lor \phi_3)$, which is in turn equivalent to $(\phi_1 \lor \phi_2 \lor \phi_3)$. \\
\begin{remark}
For two propositional variables, the associative equivalence operator functions identically to the binary propositional connective equivalence operator. For formulas with 3 or more propositional variables, however , the associative equivalence operator does not mean that each propositional variable in the list is equivalent. Instead, it means that the equivalence of the first two propositional variables in the list is equivalent to the next propositional variable in the list, and the truth value for this expression is equivalent to the next propositional variable, and so on. For example, =[p1,p2,p3] is equivalent to (p1=p2)=p3 rather than p1=p2=p3.
\end{remark}

In Appendix \ref{pseudocode appendix}, we provide the full pseudocode of the WEST program. Below we summarize only the important points to provide analysis of time and space complexity in the next section. The regular expression $R = \{R_1 | R_2 | ... | R_k\}$, where for all $1 \leq i \leq k$, $R_i \in \{$`0', `1', `S', `,'$\}^*$, is represented as a vector $R = {R_1, R_2, ..., R_k}$.

@@

If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a boolean to enable this functionality.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{-0.1in}
 \section{WEST Code Specifications} \label{specs}
  \vspace{-0.1in}
The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
{GitHub} repository. The MLTL syntax for our program is given as the context free grammar below. In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively. $\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively. Note that the last comma listed is not a typo and indeed part of the alphabet. \\
\textbf{Alphabet}: 
\begin{align*}
    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `\mbox{$>$}' ,}\\
    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
\end{align*}

@@

In the grammar, associative propositional connectives (\textit{Assoc\_Prop\_conn}) are included for the ease of the user. Given well-formed formulas $\phi_1, \phi_2, \phi_3$, the following formula in prefix notation $(\lor[\phi_1, \phi_2, \phi_3])$ is parsed into $((\phi_1 \lor \phi_2) \lor \phi_3)$, which is in turn equivalent to $(\phi_1 \lor \phi_2 \lor \phi_3)$. \\
\begin{remark}
For two propositional variables, the associative equivalence operator functions identically to the binary propositional connective equivalence operator. For formulas with 3 or more propositional variables, however, the associative equivalence operator does not mean that each propositional variable in the list is equivalent. Instead, it means that the equivalence of the first two propositional variables in the list is equivalent to the next propositional variable in the list, and the truth value for this expression is equivalent to the next propositional variable, and so on. For example, $=[p1,p2,p3]$ is equivalent to $(p1=p2)=p3$ rather than $p1=p2=p3$.
\end{remark}

In Appendix \ref{pseudocode appendix}, we provide the full pseudocode of the WEST program.
We summarize the important points to provide analysis of time and space complexity. The regular expression $R = \{R_1 | R_2 | ... | R_k\}$, where for all $1 \leq i \leq k$, $R_i \in \{$`0', `1', `S', `,'$\}^*$, is represented as a vector $R = {R_1, R_2, ..., R_k}$.

@@

If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a Boolean to enable this functionality.
